---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

Step 1
```{r, message = FALSE}
library(classdata)
head(ames)
```
The variables in the dataset are Parcel ID, Address, Style, Occupancy, Sale Date, Sale Price, Multi Sale, YearBuilt, Acreas, TotalLivingArea (sf), Bedrooms, FinishedBsmtArea (sf), LotArea(sf), AC, FirePlace, and Neighborhood. The variables types include chrs, factors, dates, and doubles.

The variable meanings:

Parcel ID: character with ID.

Address: property address in Ames, IA.

Style: factor variable detailing the type of housing.

Occupancy: factor variable of type of housing.

Sale Date: date of sale.

Sale Price: sales price (in US dollar).

Multi Sale: logical value: was this sale part of a package?

YearBuilt: integer value: year in which the house was built.

Acres: acres of the lot.

TotalLivingArea (sf): total living area in square feet.

Bedrooms: number of bedrooms.

FinishedBsmtArea (sf): total area of the finished basement in square feet.

LotArea(sf): total lot area in square feet.

AC: logical value: does the property have an AC?

FirePlace: logical value: does the property have an fireplace?

Neighborhood: factor variable - levels indicate neighborhood area in Ames.

Possible ranges for each numerical variable:

Date: 2017 to 2022

Sale Price: 0 to 20,500,000

YearBuilt: 2017 to 2022

Acres: 12

TotalLivingArea (sf): 6000

Bedrooms: 10

FinishedBsmtArea (sf): 6500

LotArea(sf): 500000

Step 2

Acres, TotalLivingArea (sf), Bedrooms, and YearBuilt are likely variables that influence Sales Price.

Step 3
```{r, message = FALSE}
summary(ames$`Sale Price`)
```
The range of Sales Price is $20,500,000.

```{r1, message = FALSE}
library(ggplot2)

ggplot(ames, aes(x = ames$`Sale Price`)) + 
  geom_histogram(binwidth = 500000) + 
  labs(title = "Histogram of Sales Price") +
  xlab("Sales Price")

```

The distribution of sales prices is right skewed with a few major outliers. There appear to be a lot of values where the Sales Price is 0.

Step 4

Nina's Work:

My chosen variable is Bedrooms. The possible range of this variable is 0-10. Most values lie around 2-5, and has a few outliers.
```{r setup1, include=TRUE}

library(ggplot2)

ggplot(ames, aes(x = Bedrooms)) + 
  geom_bar()

```

```{r setup2, include=TRUE}

library(ggplot2)

ggplot(ames, aes(x = Bedrooms, y = `Sale Price`)) + 
  geom_point()+
  coord_flip() 

```
This follows the general pattern, and doesn't describe any oddities discussed earlier.



Christopher's Work:
I made a scatter plot with x = Acresand y = Sale Price / 100000. The view was extremely zoomed out because of a couple outliers so I added filters to remove extreme values. The vast majority of properties are below 1 Acre and and cost under a 750 thousand dollars. There is a general trend of an increase in acreage leads to increased price, but there are a fair amount of outliers to this trend.

```{r}
library(dplyr)
ggplot(ames %>% filter(Acres > 0, Acres < 5, `Sale Price` < 1000000, `Sale Price` > 0), aes(x = Acres, y = `Sale Price` / 100000)) + geom_point(alpha = 0.2)
ggplot(ames %>% filter(Acres > 0, `Sale Price` > 0), aes(x = Acres, y = `Sale Price` / 100000)) + geom_point(alpha = 0.2)
summary(ames["Acres"])
```


Jamey's Work:
I made a scatter plot with x = TotalLivingArea and y = Sale Price.
But, it was incredibly zoomed out so I limited the cartesian coordinate range.
There seems to be a positive correlation between Total Living Area and Sale Price based on the graph,
although I would probably have to make a correlation matrix to confirm.
```{r setup3, include=TRUE}
ggplot(ames, aes(x = `TotalLivingArea (sf)`, y = `Sale Price`)) +
  geom_point() +
  coord_cartesian(ylim = c(100000, 500000))
```


Ryan's Work:

```{r, message = FALSE}
library(dplyr)
ames_new <- ames %>% filter(YearBuilt != 0)
summary(ames_new$`YearBuilt`)

ggplot(ames_new, aes(x = ames_new$`YearBuilt`)) + 
  geom_histogram(binwidth = 5) + 
  labs(title = "Histogram of Year Built") +
  xlab("Year Built")

```
After removing null values, the range is 1880 to 2022. The distribution of YearBuilt is skewed left and appears bimodal, with peaks around 2022 and ~1970.


```{r, message = FALSE}
library(ggplot2)
library(dplyr)

ames_new <- ames_new %>% filter(ames_new$`Sale Price` != 0)

ggplot(ames_new, aes(x = YearBuilt, y = ames_new$`Sale Price`)) +
  geom_point() +
  labs(title = "Year Built vs. Sale Price (With Major Outliers)")

```

This is the plot with outliers. It is difficult to see the trend of the rest of the data, but the major outliers are all built after 2000.

```{r, message = FALSE}
library(ggplot2)
library(dplyr)
ames_new <- ames_new %>% filter(ames_new$`Sale Price` < 1000000)

ggplot(ames_new, aes(x = YearBuilt, y = ames_new$`Sale Price`)) +
  geom_point() +
  labs(title = "Year Built vs. Sale Price (Without Major Outliers)")

```

This scatter plot shows that there is a weak positive relationship between YearBuilt and Sale Price. There appears to be a slight curve in the data, that as YearBuilt increases, sale price increases. The only oddity in step 3 was that there were a lot of values that were 0, but these scatter plots removed those values.

